SAT Competition 2020\tnoteref{title}

### 2021-01-11 paper/main.tex
variation

Finding a solution which satisfies all the hard constraints and as many soft constraints as possible,
Z3 came up with the schedule shown in Table~\ref{tab:MainZ3Schedule} (in under two hours on a single core of a \SI{2.30}{\giga\hertz} CPU).

Its not clear how unique this is. Just take the total 286 and compare to uniform split -- that's the interesting bit, perhaps.

>>>>

Finding a solution which satisfies all the hard constraints and as many soft constraints as possible,
Z3 came up with the schedule shown in Table~\ref{tab:MainZ3Schedule} (in under two hours on a single core of a \SI{2.30}{\giga\hertz} CPU).
The table is sorted by $R^S$, the time the schedule allocates to individual solvers, and skips the zero entries.
It is not clear to what degree is the obtained schedule unique and how much it relies on each solver being present and for how long.
Nevertheless, it is interesting to observe the total number of problems covered, here 286,
and compare it to the 278 achieved in Table~\ref{tab:MainUniformTimeSplit} with the uniform split and two solvers.

Amusingly, as can be seen from the ``contributes'' column, the presence of MapleLCMDistChronoBT-DL-f2trc in the schedule
is not necessary.
% The following three lines could be skipped without much harm:
All the 15 instances this solver solves under 76 seconds were already covered by the preceding three solvers.
This result, however, does not signify a bug, as Z3 was not asked to produce a schedule with a minimal number of
participating solvers.
Indeed, allowing any other solver to run for the 76 ``wasted'' seconds would not increase the overall total.
